Methodology for Assessing the State of the Practice for Domain X

### 2020-04-16 StateOfPractice/Methodology/Methodology.tex
usability

\section{User Experiments}

Describe experiments with users to assess usability, performance etc.

>>>>

\section{User Experiments}
\subsection{Usability Experiment}
Steps:
\begin {enumerate}
\item Write research questions
\item Prepare survey questions
\item Select a list of projects
\item Identify tasks for the study subjects to perform (tasks can be defined based on user category, at least one task to modify the software)
\item Select participants 
\item Survey the study subject
\item Perform tasks
\item Observe participants (take notes, record sessions)
\item Perform pairwise comparison analysis
\item Prepare Usability report
\end {enumerate}
Describe experiments with users to assess usability, performance etc.
